Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-06-14 ms.tex
did sanity checks on sims and saved simulation max Diff Flux results.

\subsubsection{Subpixel Crosshatching Simulation}

@@

The three subarrays considered are shown in Figure \ref{fig:subpixScanSimulation}.
The position at the top of the ALONG detector has the smallest amplitude of crosshatch pattern in all three directions.
We exclude reference pixels (which form a 4 pixel wide boundary around the detector) and an additional row on the bottom and top fo the array because these illuminated rows are anomalous.

>>>>

\subsubsection{Subpixel Crosshatching Simulation}\label{sec:CrosshatchSim}

@@

The three subarrays considered are shown in Figure \ref{fig:subpixScanSimulation}.
The position at the top of the ALONG detector has the smallest amplitude of crosshatch pattern in all three directions.
We exclude reference pixels (which form a 4 pixel wide boundary around the detector) and an additional row on the bottom and top of the array because these illuminated rows are anomalous.
The best-fit amplitudes are used as input to the jitter simulations in Section \ref{sec:CrosshatchSim}.
We find that the maximum flux change for a 0.1 pixel shift is 118 ppm for the nominal grism position, 108 ppm for the top of the array and 153 ppm at the full frame grism position.
